DRAFT

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

---
title: "DRAFT"
author: "Alima Dzhanybaeva"
date: "2022-10-31"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(dplyr)
library(knitr)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.

>>>>

---
title: "DRAFT"
author: "Alima Dzhanybaeva"
date: "2022-10-31"
output:
  pdf_document:
         latex_engine: xelatex
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(modelsummary)
library(dplyr)
library(knitr)
library(htmlTable)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
## 1.1 Overview of the original data.
### The original hotels-europe data includes information on price and features of hotels in 46 European cities and for 2017-2018. The data was downloaded from https://osf.io/yzntm/download.
